%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4,11pt]{article}
\usepackage{multicol}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Willem Vanhulle} & Email : \href{mailto:willemvanhulle@protonmail.com}{willemvanhulle@protonmail.com}\\
  \href{https://willemvanhulle.tech/}{willemvanhulle.tech} &
  Mobile : +32 479 080 252 \\
\end{tabular*}




%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

 \resumeSubheading
      {OTIV (Remote operation of semi-autonomous rail vehicles)}{Ghent, Belgium}
      {Mid-level software engineer (Rust, Python)}{Apr. 2024 - current}
      \resumeItemListStart
        
        \resumeItem{Distributed systems}{Work on a system to operate freight trains remotely. Create a dynamic presence detection system. Create an internal asynchronous iterator / stream toolkit. Create a crucial connectivity monitoring systems that can react to connection loss and engage emergency breaking. Manage real-time audio- and video-streams through GStreamer and WebRTC.}
        \resumeItem{Developer tools}{Smooth out integration between the Rust language-server and the Bazel build system. Lead transition from Bazel to the Cargo build system for one team. Write CI/CD pipelines from scratch. Reduced run-time of existing CI pipelines up to 95 \%.}
        \resumeItem{Mentorship}{Organised trainings on parts of the Rust programming language that are lacking in documentation. Performed thorough code reviews and coached junior colleagues.}
        \resumeItem{Tests}{Write extensive unit tests for new and existing software modules. Implement integration tests based on requirements given by railway companies.}
        \resumeItem{Native GUI}{Co-create several immersive, multi-monitor, native user-interfaces. Implement widgets representing streamed data tables. Create a geographical map widget with highlighted train routes in Rust and Slint. }
        \resumeItem{Embedded}{Write software modules interfacing with real physical controls of trains such as custom touch-screens, toggles and traction/breaking levers, running on Linux.}
      \resumeItemListEnd

    \resumeSubheading
      {Inbiose (Microbial production of speciality carbohydrates)}{Ghent, Belgium}
      {Software engineer (Rust, Python, C, R, Typescript, HTML, SCSS)}{June 2021 - January 2024}
      \resumeItemListStart
        \resumeItem{Micro-biotechnology}{Learn science behind cellular cloning of e. coli. bacteria, used for producing sugars with special health benefits. Learn process of fermentation and  down-stream processing with ion-exchange and membrane filtering. Get involved in lab activities with lab workers, operators and researchers.}
        \resumeItem{Web-development}{Create graphical web-based data collection procedure and application for the down-stream processing department. Create accompanying simple time-series and data-grid visualisation widgets with Svelte. Introduce TypeScript as a tool for creating large web applications. }
        \resumeItem{Bio-informatics}{Implement property-based unit tests in Python to verify correctness of batch operations on internal, proprietary genetic data. Extend and maintain internal tools for bio-informatics.}
        \resumeItem{Embedded systems}{Supported creation of industrial small-scale microbial fermentation robots. Interfaced with legacy hardware (more than 25 years old) and modern optical industrial sensors. Transitioned from Python to asynchronous Rust. }
        \resumeItem{Data modelling}{Analyse and model internal scientific processes. Model and construct scientific databases in PostgreSQL. Use graph-oriented databases such as Neo4j.}
        \resumeItem{Mentorship}{Assist electronics engineers in optimising internal embedded C programs for Arduino and ESP32 micro-controllers.}
      \resumeItemListEnd


\resumeSubheading{CVO (Adult and refugee high-school)}{Leuven, Belgium}{Mathematics guest lecturer (Python, \LaTeX)}{Sept. 2020 - Jan. 2021}

% \resumeItemListStart
%     \resumeItem{Automation}{Write a script in Python and LaTeX to generate arithmetic problem-sheets for students on-demand and save time during preparation of lectures.}

%     \resumeItem{Teaching}{Prepare lectures for adult students with learning difficulties or refugee status. Give introductions to the history of mathematics and latest development. Write and grade exams.}
% \resumeItemListEnd
  
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Major professional projects}
  \resumeSubHeadingListStart

      \resumeSubheading{Emergency breaking mechanism}{OTIV}{Distributed, peer-to-peer systems, back-end (Rust)}{Sept. 2024 - Mar. 2025}

        \resumeItemListStart
            \resumeItem{Heartbeat monitor}{Detects whether the connection between a remote human operator and a semi-autonomous freight train is still normal.}
            \resumeItem{Stream aggregator}{Initialise incoming (and outgoing) pub-sub, TCP data streams for assigned freight trains. Aggregate the streams, detect connection loss, initiate emergency breaking mechanism. Findings on \href{https://willemvanhulle.tech/blog}{personal blog}.}
        \resumeItemListEnd

    \resumeSubheading{Fermentation robot}{Inbiose}{Robotics, automation (Python, Rust, C)}{Oct. 2023 - April 2024}
        \resumeItemListStart
    
            \resumeItem{Serial communication abstraction layer}{Create a high-level and safe serial API in Rust for operating essential components for a fermentation robot. Implemented thorough error detection and propagation.}

            \resumeItem{Fermentation process manager}{Add nutrients and chemicals throughout a 48h biological process for growing e. coli. bacteria. Detect anomalies and stabilise with PID-control.}
    
        \resumeItemListEnd
        
   \resumeSubheading{Collaborative data-grid}{Inbiose}{Collaborative software, UX, UI design (Typescript, Svelte, SQL, HTML, SCSS)}{Apr. 2023 - Feb. 2024}
       \resumeItemListStart
       
            \resumeItem{Distributed data-frames}{Distributed, database-backed, persisted data-grid.}
            
            \resumeItem{Spreadsheet interface}{Interactive co-operative table view for lab workers to enter chemical process data with columns grouping and multiple cell types, similar to a restricted version of Google Docs.}
            
        \resumeItemListEnd



    
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Hobby projects}
    \resumeSubHeadingListStart
   
       \resumeItem{Splitting data streams (Rust)}{Created a functional asynchronous Rust combinator to split data streams / asynchronous iterators. Run-time agnostic and fully tested. Intended to be used with many, simultaneous splits. Built with low-level asynchronous primitives such as Waker, Poll and Pin. Available as a public \href{https://crates.io/crates/forked_stream}{Rust crate}.}


        \resumeItem{Smart plant pot workshop}{Organise and co-lead a workshop on creating a smart plant pot watering system with a Raspberry Pi Pico / ESP32c6, Rust and async Embassy. Integrated USB serial communication and debugging (with JTAG or hardware debug probes), analogue sensing and wireless network notifications. Event at \href{https://www.meetup.com/systems-programming-ghent/events/307269551}{MeetUp}.}


  \resumeSubHeadingListEnd


%
%--------PROGRAMMING SKILLS------------
\section{Spoken languages}
   \resumeSubHeadingListStart


   
        \resumeSubItem{English, Dutch}{Native.}
        \resumeSubItem{French, German}{Intermediate.}

    \resumeSubHeadingListEnd
      
\section{Programming languages}
    \resumeSubHeadingListStart    
        \resumeItem{Rust}{Advanced (2 years). Specialized in  complex trait bounds and creating performant asynchronous combinators from scratch. Frameworks used: Axum (web server), Embassy and Tokio (asynchronous runtimes),  Zenoh (publish-subscribe), Serde (serialization), Statig (state machines), Prost (protobuf). Limited experience with embedded HALs.} 

        \resumeItem{Coq, Agda, Haskell}{Intermediate (3 years). Used several proof-assistants for formal mathematics (topology) / systems software verification. Following up recent developments in free-time.}
        
        \resumeItem{HTML, SASS, TypeScript, JavaScript, SQL}{Advanced (3 years).  Express.js back-end, Svelte(Kit) front-end.}  
        
        \resumeItem{Python}{Advanced (6 years). Bio-informatics with BioPython. End-to-end UI testing. Used property-based testing with Hypothesis (fuzzer).}
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KU Leuven}{Leuven, Belgium}
      {Preparation program and Master of Science in Theoretical Physics (terminated early)}{Sep. 2019 -- April 2021}
    \resumeItemListStart
        \resumeItem{Completed courses}{Statistical mechanics, data mining and neural networks, thermodynamics, analytical mechanics, electrodynamics.}
        \resumeItem{Volunteering roles}{Guide for international students.}
    \resumeItemListEnd
    \resumeSubheading
      {KU Leuven}{Leuven, Belgium}
      {Master of Science in Pure Mathematics (Eng.), thesis on functional progr. lang.}{Sep. 2017 -- June 2019}
    \resumeItemListStart
        \resumeItem{Completed courses}{Algebra, analysis, discrete mathematics, differential geometry, unified geometry, topology.}
        \resumeItem{Volunteering roles}{Coordinator of Groot-Begijnhof Leuven student association.}
    \resumeItemListEnd
    \resumeSubheading
      {VUB}{Brussels, Belgium}
      {Bachelor of Science in Mathematics, Minor Computer Science, thesis on unsupervised learning}{Sep. 2013 -- Aug. 2017}
        \resumeItemListStart
            \resumeItem{Completed courses}{Functional programming, algorithms and data-structures, logic, analysis, algebra, philosophy, geometry.}
            \resumeItem{Student job}{Mathematics tutor.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd



\section{Hobbies}

\resumeSubHeadingListStart

\resumeItem{Community founder}{Founder of ``Systems Programming Ghent'' (\href{https://sysghent.be}{sysghent.be}): organise networking events, in-depth talks and workshops in Ghent about systems programming languages such as Rust and C++.}

\resumeItem{Play with electronical components}{Order development boards and assemble simple electronical circuits with simple sensors. Some experience with ARM and RISC-V boards such as ESP32c6, Arduino Uno (AVR), Raspberry Pico (RP2040).}
 
\resumeItem{Visit developer conferences}{I go to the developer conferences in Europe to meet colleagues and share my passion.}

\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
